Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-02-08 pkg/disttree/inst/draft/draft.Rnw
edited reference for GLM
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1992 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d9c1a42add31205b35ba4fbb6c3d6f922ea74101

In regression analysis various models have been developed to describe the
relationship between a response variable and a set of covariates. The classical
model is the linear model (LM) where the conditional mean of the response
is modeled through a linear function of the covariates (see the left panel of
Figure~\ref{Devel_parmod} for a schematic illustration). Over the last decades
this has been extended in various directions including:
\begin{itemize}
  \item Generalized linear models (GLMs, \citealp{McCullagh+Nelder:1983})
    encompassing an additional nonlinear link function for the conditional mean.
  \item Generalized additive models (GAMs, \citealp{Hastie+Tibshirani:1986})
    allowing for smooth nonlinear effects in the covariates
    (Figure~\ref{Devel_parmod}, middle).
  \item Generalized additive models for location, scale, and shape
    (GAMLSS, \citealt{stasinopoulos2005}) adopting a probabilistic modeling
    approach. In GAMLSS, each parameter of a statistical distribution can depend
    on an additive predictor of the covariates comprising linear and/or
    smooth nonlinear terms (Figure~\ref{Devel_parmod}, right).
\end{itemize}
Thus, the above-mentioned models provide a broad toolbox for capturing different
aspects of the response (mean only vs.\ full distribution) and different types
of dependencies on the covariates (linear vs.\ nonlinear additive terms).

>>>>

In regression analysis various models have been developed to describe the
relationship between a response variable and a set of covariates. The classical
model is the linear model (LM) where the conditional mean of the response
is modeled through a linear function of the covariates (see the left panel of
Figure~\ref{Devel_parmod} for a schematic illustration). Over the last decades
this has been extended in various directions including:
\begin{itemize}
  \item Generalized linear models (GLMs, \citealp{McCullagh+Nelder:1983})
    encompassing an additional nonlinear link function for the conditional mean.
  \item Generalized additive models (GAMs, \citealp{Hastie+Tibshirani:1989})
    allowing for smooth nonlinear effects in the covariates
    (Figure~\ref{Devel_parmod}, middle).
  \item Generalized additive models for location, scale, and shape
    (GAMLSS, \citealt{stasinopoulos2005}) adopting a probabilistic modeling
    approach. In GAMLSS, each parameter of a statistical distribution can depend
    on an additive predictor of the covariates comprising linear and/or
    smooth nonlinear terms (Figure~\ref{Devel_parmod}, right).
\end{itemize}
Thus, the above-mentioned models provide a broad toolbox for capturing different
aspects of the response (mean only vs.\ full distribution) and different types
of dependencies on the covariates (linear vs.\ nonlinear additive terms).
